---
output:
  pdf_document: default
  html_document: default
---
```{r}
library(forecast)
armax_fc = function(tsdata,ntrain,order,method,traincoef,include.mean,xreg,
                    iprint=F){
              
              obj <<-arima(tsdata,order=order,init=traincoef,fixed=traincoef,
              # next line for debugging, after debugging, replace with above line
              # obj <<- arima(tsdata,order=order,init=traincoef,fixed=traincoef,
              method=method, include.mean=include.mean, xreg=xreg,
              optim.control=list(maxit=0))
              # yt = y_{t|t-1} + innov ; fc = yt-innov
              fc = tsdata- obj$residuals
              
              ntotal = length(tsdata)
              holdout_fc = fc[(ntrain+1):ntotal]
              holdout = tsdata[(ntrain+1):ntotal]
              
              if(iprint) print(cbind(holdout,holdout_fc))
              rmse = sqrt(mean((holdout-holdout_fc)^2))
              list(rmse=rmse, fc=holdout_fc)
              }

arima_fc = function(tsdata,ntrain,order,method,traincoef,include.mean,
                    iprint=F){
  
  obj <<-arima(tsdata,order=order,init=traincoef,fixed=traincoef,
               # next line for debugging, after debugging, replace with above line
               # obj <<- arima(tsdata,order=order,init=traincoef,fixed=traincoef,
               method=method, include.mean=include.mean,
               optim.control=list(maxit=0))
  # yt = y_{t|t-1} + innov ; fc = yt-innov
  fc = tsdata- obj$residuals
  
  ntotal = length(tsdata)
  holdout_fc = fc[(ntrain+1):ntotal]
  holdout = tsdata[(ntrain+1):ntotal]
  
  if(iprint) print(cbind(holdout,holdout_fc))
  rmse = sqrt(mean((holdout-holdout_fc)^2))
  list(rmse=rmse, fc=holdout_fc)
}

```


```{r}
train = read.csv("DailyDelhiClimateTrain.csv")
test = read.csv("DailyDelhiClimateTest.csv")

y_train = ts(train$meantemp, frequency = 365, start=c(2013,1))
x1_train = ts(train$humidity, frequency = 365, start=c(2013,1))
x2_train = ts(train$wind_speed, frequency = 365, start=c(2013,1))
x3_train = ts(train$meanpressure, frequency = 365, start=c(2013,1))

y_test = ts(test$meantemp, frequency = 365, start=c(2017,1))
x1_test = ts(test$humidity, frequency = 365, start=c(2017,1))
x2_test = ts(test$wind_speed, frequency = 365, start=c(2017,1))
x3_test = ts(test$meanpressure, frequency = 365, start=c(2017,1))

library(forecast)
y_diff <- diff(y_train)
plot(y_train)
plot(y_diff)

acf(y_diff, main = "ACF of meantemp after differencing")
acf(y_train, main = "ACF of meantemp before differencing")
pacf(y_train, main = "PACF of meantemp before diff")
pacf(y_diff, main = "PACF of meantemp after diff")

ccf(y_diff, x1_train, main = "CCF between y and x1")
ccf(y_diff, x2_train, main = "CCF between y and x2")
ccf(y_diff, x3_train, main = "CCF between y and x3")

ccf(y_train, x1_train, main = "CCF between y and x1")
ccf(y_train, x2_train, main = "CCF between y and x2")
ccf(y_train, x3_train, main = "CCF between y and x3")
```
#suggested practice: 
#no seasonality, do ARIMAX, possible ARIMA terms in residuals

```{r}
total = rbind(train,test)
df2 = data.frame("y" = total$meantemp, "x1" = total$humidity,"x2" = total$wind_speed,"x3" = total$meanpressure)
ntotal = 1575
ntrain = 1462

df_lag1regression = data.frame(
  y= df2$y[2:(ntotal)],
  x1prev=df2$x1[1:(ntotal-1)],
  x2prev=df2$x2[1:(ntotal-1)],
  x3prev=df2$x3[1:(ntotal-1)]
  )

#regression_fit on the training set
reg1 = lm(y~ x1prev+x2prev+x3prev, data=df_lag1regression[1:(ntrain),])
print(summary(reg1))

#x3 coeffecients is not significant, dropping the term
reg2 = lm(y~ x1prev+x2prev, data=df_lag1regression[1:(ntrain),])
print(summary(reg2))

#residuals reg1
resid_reg1 = reg1$residuals
plot.ts(resid_reg1)
acf(resid_reg1)
pacf(resid_reg1)

plot.ts(diff(resid_reg1))
acf(diff(resid_reg1))
pacf(diff(resid_reg1))

resid1_auto = auto.arima(resid_reg1)
print(resid1_auto)

#residuals reg2
resid_reg2 = reg2$residuals
plot.ts(resid_reg2)
acf(resid_reg2)
pacf(resid_reg2)

plot.ts(diff(resid_reg2))
acf(diff(resid_reg2))
pacf(diff(resid_reg2))

resid2_auto = auto.arima(resid_reg2)
print(resid2_auto)
```

#Using 2 regressors suggest regressing on previous X1, X2, with ARIMA(2,1,2) residual


#refitting the ARIMAX model: using previous X1 and X2, and ARIMA(2,1,1) residual
```{r}
train_arx = arima(
                df_lag1regression$y[1:ntrain], 
                order=c(2,1,2), 
                method="CSS",
                include.mean=T, 
                xreg=cbind(df_lag1regression$x1[1:ntrain],df_lag1regression$x2[1:ntrain])
                )

print(train_arx)


#Additional Tries:
#Using sinusoid trend terms
day=c(1:1462)
day_test=c(1:114)

train_df = data.frame(y=df_lag1regression$y[1:ntrain], day=c(1:1462),
                      cosine=cos(2*pi*day/365), sine=sin(2*pi*day/365))
holdout_df = data.frame(y=test$meantemp, day=c(1:114),
                        cosine=cos(2*pi*day_test/365), sine=sin(2*pi*day_test/365))
reg_sinusoid = lm(y~ cosine+sine, data=train_df)


summary(reg_sinusoid)
resid = reg_sinusoid$residuals
resid_auto = auto.arima(resid)
print(resid_auto)

#test RMSE
pred_holdout = predict(reg_sinusoid,newdata=holdout_df)
resid_holdout = test$meantemp-pred_holdout

residuals_total = c(reg_sinusoid$residuals,resid_holdout)

sinusoid_result = arima_fc(residuals_total,1462,order = c(2,1,1),"CSS",include.mean = T,resid_auto$coef)
sinusoid_result$rmse

plot(y_test[1:112], type = "l", col = "blue", lwd = 2,
     main = "Prediction vs True Test Values",
     ylab = "Value", xlab = "Time")

lines(sinusoid_result$fc + pred_holdout, col = "red", lwd = 2)

legend("topleft",
       legend = c("True", "Predicted"),
       col = c("blue", "red"),
       lwd = 2)
```













#Using mixing terms
df_lag1_mixed_regression = data.frame(
  y= df2$y[2:(ntotal)],
  x1prev=df2$x1[1:(ntotal-1)],
  x2prev=df2$x2[1:(ntotal-1)],
  x3prev=df2$x3[1:(ntotal-1)],
  X1X2  =df2$x1[1:(ntotal-1)] * df2$x2[1:(ntotal-1)],
  X1X3  =df2$x1[1:(ntotal-1)] * df2$x3[1:(ntotal-1)]
)

#regression_fit on the training set
reg_mixed = lm(y~ x1prev+x2prev+x3prev+X1X2+X1X3, data=df_lag1_mixed_regression[1:(ntrain),])
print(summary(reg_mixed))

reg_mixed_2 = lm(y~ x1prev+x3prev+X1X3, data=df_lag1_mixed_regression[1:(ntrain),])
print(summary(reg_mixed_2))

resid3_auto = auto.arima(reg_mixed_2$residuals)
print(resid2_auto)

train_arx_mixed = arima(
  df_lag1_mixed_regression$y[1:ntrain], 
  order=c(2,1,2), 
  method="CSS",
  include.mean=T, 
  xreg=cbind(df_lag1_mixed_regression$x1[1:ntrain],df_lag1_mixed_regression$x3[1:ntrain],df_lag1_mixed_regression$X1X3[1:ntrain])
)

print(train_arx_mixed)
armax_result_mixed = armax_fc(
                        df_lag1_mixed_regression$y,
                        ntrain = ntrain, 
                        order = c(2,1,2),
                        method = "CSS",
                        traincoef = train_arx_mixed$coef,
                        include.mean = T,
                        xreg =cbind(
                          df_lag1_mixed_regression$x1prev,
                          df_lag1_mixed_regression$x3prev,
                          df_lag1_mixed_regression$X1X3))

pred_xreg_mixed = armax_result_mixed$fc
testrmse_mixed  = armax_result_mixed$rmse
print(testrmse_mixed)












#print predictions and test rmse
armax_result = armax_fc(
        df_lag1regression$y,ntrain = ntrain, order = c(2,1,2),method = "CSS",
         traincoef = train_arx$coef,include.mean = T,xreg =cbind(df_lag1regression$x1prev,df_lag1regression$x2prev))

pred_xreg = armax_result$fc
testrmse  = armax_result$rmse
print(testrmse)

plot(y_test[1:112], type = "l", col = "blue", lwd = 2,
     main = "Prediction vs True Test Values",
     ylab = "Value", xlab = "Time")

lines(armax_result$fc, col = "red", lwd = 2)

legend("topleft",
       legend = c("True", "Predicted"),
       col = c("blue", "red"),
       lwd = 2)
